Decentralized autonomous organization to manage a trust\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-05 paper/Paper.tex
fix price function in paper
clearify text
Corrections to WP

After $t_p$ has passed, any token holder can call a function in the DAO contract that will verify that the majority voted in favor of the proposal and that quorum was reached; the function will execute the proposal if this is the case. If this is not the case, the proposal will be closed. The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
\begin{equation}
 q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{total}})}
 \label{minQuorum}
\end{equation}
Where $d$ is the \verb|minQuorumDivisor|. This parameter’s default value is $5$, but it will double in the case the quorum has not been met for over a year.
$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward token as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}). The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received.

@@

A problem this simple fix doesn’t address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely. An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some of them could be unaware of the situation and won't do this. For the DAO to be considered safe, it is required that inactive token holders will not lose their funds. Our proposed solution is implemented by limiting each individual DAO to a single service provider. This service provider controls the only account that can receive ether from the DAO, across all proposals. In addition, the service provider can build a “whitelist” of addresses that the DAO is allowed to send funds to. This gives the service provider of the DAO considerable power. To prevent the abuse of this power, it is possible for the DAO to vote for a new service provider, which may result in a split of the DAO as described above.

@@

The process of choosing a new service provider is as follows:
Any token holder can start a proposal to vote for a new service provider. For this proposal there is no proposal deposit to be paid, otherwise the attacker could vote for an extremely high deposit, preventing any splits. The debating period for this proposal is $10$ days.
This is $4$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through. There is no quorum requirement, so that every token holder has the ability to split into their own DAO. 
The debating period is used to discuss the new service provider and conduct an informal vote. The result of the vote has no actual consequence, it is purely instructional. After this first voting round, token holders can cast a second vote to confirm the result. In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.

\section{Token Price} \label{TokenPrice}
In order to reward contributors who purchase tokens early during the funding period, since they had less information, and hence a greater risk, than contributors who joined later, they will pay less than contributors who joined later.
For the DAO described here, we have chosen the following price schedule:
\begin{equation}
 P(t) = \begin{cases}
0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
0.01 + 0.005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
0.015 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
This results in a constant price in the beginning, until $2$ weeks before the end of the token sale. At this time the price increased daily by $0.005 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.
\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.

>>>>

After $t_p$ has passed, any token holder can call a function in the DAO contract that will verify that the majority voted in favor of the proposal and that quorum was reached; the function will execute the proposal if this is the case. If this is not the case, the proposal will be closed. The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
\begin{equation}
 q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{total}})}
 \label{minQuorum}
\end{equation}
Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward token as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}). The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received.

@@

A problem this simple fix doesn't address is voter apathy: some token holders might not be actively involved in the DAO and might not follow proposals closely. An attacker could use this to their advantage. Even though the minority has the chance to retrieve their funds and split the DAO, some of them could be unaware of the situation and won't do this. For the DAO to be considered safe, it is required that inactive token holders will not lose their funds. Our proposed solution is implemented by limiting each individual DAO to a single service provider. This service provider controls the only account that can receive ether from the DAO, across all proposals. In addition, the service provider can build a “whitelist” of addresses that the DAO is allowed to send funds to. This gives the service provider of the DAO considerable power. To prevent the abuse of this power, it is possible for the DAO to vote for a new service provider, which may result in a split of the DAO as described above.

@@

The process of choosing a new service provider is as follows:
Any token holder can start a proposal to vote for a new service provider. For this proposal there is no proposal deposit to be paid, otherwise the attacker could vote for an extremely high deposit, preventing any splits. The debating period for this proposal is $10$ days.
This is $4$ days less than the minimum required for regular proposals, allowing anyone to retrieve their funds before a potentially malicious proposal goes through. There is no quorum requirement, so that every token holder has the ability to split into their own DAO. 
The debating period is used to discuss (on or off-chain) the new service provider and conduct a first vote that's non-binding. After this first vote, token holders can cast a second one to confirm its results. In the case a majority opts to  keep the original service provider, the minority can either change their vote to keep the original service provider in order to avoid a split, or inversely they can confirm their vote for a new service provider and move their portion of the funds to a new DAO.

\section{Token Price} \label{TokenPrice}
DAO Token price increases over time.  This reflects an assumption that early purchasers have greater risk, as they may have less information about the potential success of the DAO and do not know whether follow-on contribution will lead to full funding of the DAO.  
For the DAO described here, we have chosen the following price schedule:
\begin{equation}
 P(t) = \begin{cases}
0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
0.01 + 0.0005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
0.015 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
This results in a constant price in the beginning, until $2$ weeks before the end of the token sale. At this time the price increased daily by $0.005 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.

@@

\subsubsection*{withdrawRewardFor}
This function is used to retrieve the portion of the rewards in the \verb|rewardAccount| which belong to address given in the parameter.
Their portion of the reward tokens $S$ is calculated as follows:
\begin{equation}
 S = R_{\text{DAO}} \cdot T_{\text{sender}} / T_{\text{total}} + R_{\text{sender}}
\end{equation}
Here $R_{\text{DAO}}$ is the amount of reward tokens owned by the DAO, and $T_{\text{sender}}$ the amount of DAO tokens which are directly owned by the sender. $R_{\text{sender}}$ will always be zero except in the case that the sender is a DAO that has split from the original DAO and owns their own reward tokens from the split.
The amount of ether $\Xi_{\text{reward}}$ which is then sent to the DAO token holder that calls this function is:
\begin{equation}
\Xi_{\text{reward}} = \Xi_{\text{rewardAccount}} \cdot S / R_{\text{total}} - \Xi_{\text{paidOut[sender]}}
\end{equation}
Here $\Xi_{\text{rewardAccount}}$ is the total rewards ever received by the \verb|rewardAccount|, $R_{\text{total}}$ is the total amount of reward tokens that have ever been created, regardless of splits (\verb|totalRewardToken|) and $\Xi_{\text{paidOut[sender]}}$ is the total amount of wei which has already been paid out to the DAO token holder calling the function. The reward tokens are further elaborated in section \ref{split}.
\subsubsection*{addAllowedAddress}
This function adds an address to the whitelist, \verb|allowedRecipients|. It can only be executed by the service provider.
